Model Search in Relational Domains

### 2016-10-22 example.tex
edits Sec 2

Let us consider a simple program in Figure~\ref{fig:example}, which performs
multiplication of machine integers and checks that the result is always
positive.  To avoid overflow error, we assume that the input $v$ has an
upper bound~$N$.  The control-flow graph is given in the middle column of
Figure~\ref{fig:example}.

We analyse the program using three different analysers -- {\em bounded 
model checking (BMC)}, {\em abstract interpretation} and {\em ACDCL}.    
%
\Omit {
The SAT solver makes 36 decisions, 1365 Boolean constraint propagations 
and performs 5 conflict analysis with 65 conflict literals.  Moreover, 
the solver performs a restart, presumably to recover from bad decisions.  
}
%
Standard forward interval analysis is too imprecise to verify the
safety of the above program.  The imprecision is due to control-flow join at
node $n4$.  A state-of-the-art abstract interpretation tool,
Astr{\'e}e~\cite{se2011}, requires external hints, provided by manually
annotating the code with partition directives at $n1$, to prove safety.  The
partition directive tells the tool to analyse each program execution path
separately.  To determine safety, Astr{\'e}e requires a product of a trace
partitioning domain and an interval domain or a relational domain
such as octagons.
%
\Omit { In general, the imprecision is either intended by the tool because such
high precision analysis is normally not required for runtime error analysis
or the imprecision is unavoidable due to the complexity of the application
under analysis.
}

>>>>

Let us consider a simple program in Figure~\ref{fig:example}, which performs
multiplication of machine integers and checks that the result is always
positive.  To avoid overflow, we assume that the input $v$ has an upper
bound~$N$.  The control-flow graph is given in the middle column of
Figure~\ref{fig:example}.  We apply three different analysis techniques:
1)~{\em bounded model checking (BMC)}, 2)~{\em abstract interpretation} and
3)~{\em ACDCL}.

%
\Omit {
The SAT solver makes 36 decisions, 1365 Boolean constraint propagations 
and performs 5 conflict analysis with 65 conflict literals.  Moreover, 
the solver performs a restart, presumably to recover from bad decisions.  
}
%
Standard forward interval analysis is too imprecise to verify the
safety of the above program.  The imprecision is due to control-flow join at
node $n4$.  A state-of-the-art abstract interpretation tool,
Astr{\'e}e~\cite{se2011}, requires external hints, provided by manually
annotating the code with partition directives at $n1$, to prove safety.  The
partition directive tells the tool to analyse each program execution path
separately.  To determine safety, Astr{\'e}e requires a product of a trace
partitioning domain and an interval domain or a relational domain
such as octagons.
%
\Omit { In general, the imprecision is either intended by the tool because such
high precision analysis is normally not required for runtime error analysis
or the imprecision is unavoidable due to the complexity of the application
under analysis.
}
